The low-frequency environment of the Murchison Widefield Array: radio-frequency interference analysis and mitigation

### 2014-11-17 articles/2014/MWA-Radio-Environment/mwa-radio-environment.tex
Changing text of Miriad, as it uses the SIR-operator

The \textsc{aoflagger} RFI detection strategy, originally developed for LOFAR, works well for the MWA. Faint RFI events such as the ones in Figs.~\ref{fig:broadband-pulse} and \ref{fig:156_7}, or complex events such as the one in Fig.~\ref{fig:dvb-burst}, are not adequately detected by a single-sample thresholding algorithm, but \textsc{aoflagger}'s SumThreshold and SIR-operator algorithms are able to flag such events. These algorithms have gained some popularity; besides the use of \textsc{aoflagger} by individual astronomers, the SumThreshold algorithm is implemented in the pipeline for eMERLIN \citep{serpent-peck-2013} and in \textsc{miriad}'s PGFLAG task. Nevertheless, other projects still use single-sample thresholding, e.g. PAPER \citep{parsons-paper-eorlimit-2014}. Since strong RFI is seen practically everywhere, and because the apparent strength of RFI events will follow a power-law distribution, many faint transmitters will interfere with observations of any (terrestrial) radio observatory. Using algorithms with low sensitivity will detect fewer of these, and thus result in RFI becoming more quickly a problem in long-integration projects.

>>>>

The \textsc{aoflagger} RFI detection strategy, originally developed for LOFAR, works well for the MWA. Faint RFI events such as the ones in Figs.~\ref{fig:broadband-pulse} and \ref{fig:156_7}, or complex events such as the one in Fig.~\ref{fig:dvb-burst}, are not adequately detected by a single-sample thresholding algorithm, but \textsc{aoflagger}'s SumThreshold and SIR-operator algorithms are able to flag such events. These algorithms have gained some popularity; besides the use of \textsc{aoflagger} by individual astronomers, \textsc{miriad}'s PGFLAG task implements both the SumThreshold and SIR-operator algorithms, and the pipeline for eMERLIN \citep{serpent-peck-2013} implements the SumThreshold algorithm. Nevertheless, other projects still use single-sample thresholding, e.g. PAPER \citep{parsons-paper-eorlimit-2014}. Since strong RFI is seen practically everywhere, and because the apparent strength of RFI events will follow a power-law distribution, many faint transmitters will interfere with observations of any (terrestrial) radio observatory. Using algorithms with low sensitivity will detect fewer of these, and thus result in RFI becoming more quickly a problem in long-integration projects.
